\textbf{SPECFEM3D Cartesian}\\ \textbf{User Manual}

### 2016-07-11 doc/USER_MANUAL/09_noise_simulations.tex
updates doc

\item Before we can run noise simulations, we have to specify the noise
statistics, e.g., the ensemble-averaged noise spectrum. Matlab scripts
are provided to help you to generate the necessary file:
\texttt{EXAMPLES/noise\_tomography/NOISE\_TOMOGRAPHY.m} (main program)\\
\texttt{EXAMPLES/noise\_tomography/PetersonNoiseModel.m}

@@

\texttt{DT} is given in \texttt{Par\_file}, but \texttt{NSTEP} is
NOT the one specified in \texttt{Par\_file}. Instead, you have to
feed $2~\mathrm{NSTEP}-1$ to account for the doubled length of cross
correlations. \texttt{Tmin} and \texttt{Tmax} correspond to the period
range you are interested in, whereas \texttt{NOISE\_MODEL} denotes
the noise model you will be using. Details can be found in the Matlab
script.

After running the Matlab script, you will be given the following information
(plus a figure in Matlab):
\begin{verbatim}
*************************************************************
the source time function has been saved in:
..../S_squared (note this path must be different)
S_squared should be put into directory:
OUTPUT_FILES/NOISE_TOMOGRAPHY/ in the SPECFEM3D Cartesian package
\end{verbatim}

@@

\item Create a new directory in the SPECFEM3D Cartesian package, name it
as \texttt{OUTPUT\_FILES/NOISE\_TOMOGRAPHY/}. We will add some parameter
files later in this folder.
\item Put the Matlab-generated-file \texttt{S\_squared} in \texttt{OUTPUT\_FILES/NOISE\_TOMOGRAPHY/}.

That's to say, you will have a file \texttt{OUTPUT\_FILES/NOISE\_TOMOGRAPHY/S\_squared}
in the SPECFEM3D Cartesian package.

\item Create a file called \texttt{OUTPUT\_FILES/NOISE\_TOMOGRAPHY/irec\_master\_noise}.
Note that this file is located in directory \texttt{OUTPUT\_FILES/NOISE\_TOMOGRAPHY/}
as well. In general, all noise simulation related parameter files
go into that directory. \texttt{irec\_master\_noise} contains only
one integer, which is the ID of the `master' receiver. For example,
if this file contains 5, it means that the fifth receiver listed in
\texttt{DATA/STATIONS} becomes the `master'. That's why we mentioned
previously that the order of receivers in \texttt{DATA/STATIONS} is
important.

Note that in regional simulations, the \texttt{DATA/STATIONS} might
contain receivers which are outside of our computational domains.
Therefore, the integer in \texttt{irec\_master\_noise} is actually
the ID in \texttt{DATA/STATIONS\_FILTERED} (which is generated by
\texttt{bin/xgenerate\_databases}).

\item Create a file called \texttt{OUTPUT\_FILES/NOISE\_TOMOGRAPHY/nu\_master}.
This file holds three numbers, forming a (unit) vector. It describes
which component we are cross-correlating at the `master' receiver,
i.e., ${\hat{{\bf \nu}}}^{\alpha}$ in \citet{trompetal2010}. The
three numbers correspond to E/N/Z components respectively. Most often,
the vertical component is used, and in those cases the three numbers
should be 0, 0 and 1.
\item Describe the noise direction and distributions in \texttt{src/shared/noise\_tomography.f90}.
Search for a subroutine called \texttt{noise\_distribution\_direction}
in \texttt{noise\_tomography.f90}. It is actually located at the very
beginning of \texttt{noise\_tomography.f90}. The default assumes vertical
noise and a uniform distribution across the whole free surface of
the model. It should be quite self-explanatory for modifications.
Should you modify this part, you have to re-compile the source code.
\end{itemize}

@@

\end{itemize}
Note that it is better to run the three steps continuously within
the same job, otherwise you have to collect the saved surface movies
from the old nodes/CPUs to the new nodes/CPUs. This process varies
from cluster to cluster and thus cannot be discussed here. Please
ask your cluster administrator for information/configuration of the
cluster you are using.\\

>>>>

\item Before we can run noise simulations, we have to specify the noise
statistics, e.g., the ensemble-averaged noise spectrum. Matlab scripts
are provided to help you to generate the necessary file:
\begin{verbatim}
EXAMPLES/noise_tomography/NOISE_TOMOGRAPHY.m  (main program)
EXAMPLES/noise_tomography/PetersonNoiseModel.m
\end{verbatim}

@@

\texttt{DT} is given in \texttt{Par\_file}, but {\color{red} \texttt{NSTEP} is
NOT the one specified in \texttt{Par\_file}}. {\bf Instead, you have to
feed $2~\mathrm{NSTEP}-1$ to account for the doubled length of cross
correlations}. \texttt{Tmin} and \texttt{Tmax} correspond to the period
range you are interested in, whereas \texttt{NOISE\_MODEL} denotes
the noise model you will be using 
(\texttt{'NLNM'} for New Low Noise Model or \texttt{'NHNM'} for New High Noise Model). 
Details can be found in the Matlab script.

After running the Matlab script, you will be given the following information
(plus a figure in Matlab):
\begin{verbatim}
*************************************************************
the source time function has been saved in:
..../S_squared (note this path must be different)
S_squared should be put into directory:
./NOISE_TOMOGRAPHY/ in the SPECFEM3D Cartesian package
\end{verbatim}

@@

\item Create a new directory in the SPECFEM3D Cartesian package, name it
as \texttt{./NOISE\_TOMOGRAPHY/}. We will add some parameter
files later in this folder.

\item Put the Matlab-generated-file \texttt{S\_squared} in \texttt{./NOISE\_TOMOGRAPHY/}.

That's to say, you will have a file \texttt{./NOISE\_TOMOGRAPHY/S\_squared}
in the example provided in the SPECFEM3D Cartesian package.

\item Create a file called \texttt{./NOISE\_TOMOGRAPHY/irec\_master\_noise}.
Note that this file is located in directory \texttt{./NOISE\_TOMOGRAPHY/}
as well. In general, all noise simulation related parameter files
go into that directory. \texttt{irec\_master\_noise} contains only
one integer, which is the ID of the `master' receiver. For example,
if this file contains 5, it means that the fifth receiver listed in
\texttt{DATA/STATIONS} becomes the `master'. That's why we mentioned
previously that the order of receivers in \texttt{DATA/STATIONS} is
important.

Note that in some simulations, the \texttt{DATA/STATIONS} might
contain receivers which are outside of our computational domains.
Therefore, the integer in \texttt{irec\_master\_noise} is actually
the ID in \texttt{DATA/STATIONS\_FILTERED} (which is generated by
\texttt{bin/xgenerate\_databases}).

\item Create a file called \texttt{./NOISE\_TOMOGRAPHY/nu\_master}.
This file holds three numbers, forming a (unit) vector. It describes
which component we are cross-correlating at the `master' receiver,
i.e., ${\hat{{\bf \nu}}}^{\alpha}$ in \citet{trompetal2010}. The
three numbers correspond to E/N/Z components respectively. Most often,
the vertical component is used, and in those cases the three numbers
should be 0, 0 and 1.

\item Describe the noise direction and distributions in \texttt{src/specfem3d/noise\_tomography.f90}.
Search for a subroutine called \texttt{noise\_distribution\_direction}
in \texttt{noise\_tomography.f90}. It is actually located at the very
beginning of \texttt{noise\_tomography.f90}. The default assumes vertical
noise and a uniform distribution across the whole free surface of
the model. It should be quite self-explanatory for modifications.
Should you modify this part, you have to re-compile the source code.
\end{itemize}

@@

\end{itemize}

It is better to run the three steps continuously within
the same job on a cluster, otherwise you have to collect the saved surface movies
from the old nodes to the new nodes. This process varies
from cluster to cluster and thus cannot be discussed here. Please
ask your cluster administrator for information/configuration of the
cluster you are using.\\
